### 2016-02-08 Manuscript/Table_results.tex
color testings

% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Sat Jun 20 17:41:32 2015

@@

  \textbf{Afrosoricida} & \textbf{species} & \textbf{23/42} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & \textbf{1.89*} & \textbf{1.19} \\ 
  Carnivora & family & 11/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.43 & 1.68 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{30/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.14**} & \textbf{1.81*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{42/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{18.64**} & \textbf{3.02**} \\ 

@@

  \textbf{Cetartiodactyla} & \textbf{genus} & \textbf{77/128} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & \textbf{0.87} & \textbf{1.77*} \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{129/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{2.72*} & \textbf{0.04} \\ 
  Chiroptera & family & 13/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & 0.55 & 0.63 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{85/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{16.91**} & \textbf{2.85**} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{165/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{14.55**} & \textbf{3.44**} \\ 

@@

  \textbf{Pholidota} & \textbf{species} & \textbf{3/8} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & \textbf{2.64*} & \textbf{2.23*} \\ 
  Pilosa & family & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & 0.94 & 0.93 \\ 
  Pilosa & genus & 3/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.36 & -0.31 \\ 
  Pilosa & species & 3/29 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & 0.33 & 0.79 \\ 

@@

  Proboscidea & genus & 1/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar68.pdf} &   &   \\ 
  Proboscidea & species & 1/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar69.pdf} &   &   \\ 
  Rodentia & family & 11/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & -0.46 & -1.91 \\ 
  Rodentia & genus & 21/450 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -2.11 & 0.3 \\ 
  Rodentia & species & 15/2094 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & -1.65 & -2.55 \\ 

>>>>

% latex table generated in R 3.2.3 by xtable 1.8-0 package
% Mon Feb  8 17:25:14 2016

@@

  Afrosoricida & species & 23/42 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & 1.75 & 1.08 \\ 
  Carnivora & family & 14/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.63 & 0.6 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{54/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.81**} & \textbf{1.78*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{76/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{7.66**} & \textbf{0.85} \\ 

@@

  Cetartiodactyla & genus & 100/128 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & 0.85 & 0.94 \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{171/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{1.92*} & \textbf{-0.46} \\ 
  Chiroptera & family & 15/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & -0.28 & 0.56 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{93/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{13.47**} & \textbf{1.1} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{215/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{8.82**} & \textbf{1.22} \\ 

@@

  Pholidota & species & 4/8 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & 1.18 & 0.94 \\ 
  Pilosa & family & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & 1.87 & 2 \\ 
  Pilosa & genus & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.96 & 0.36 \\ 
  \textbf{Pilosa} & \textbf{species} & \textbf{5/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & \textbf{1.28} & \textbf{2.38**} \\ 

@@

  Proboscidea & genus & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar68.pdf} &   &   \\ 
  Proboscidea & species & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar69.pdf} & -0.69 & -0.69 \\ 
  Rodentia & family & 18/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & 0.66 & -0.98 \\ 
  Rodentia & genus & 82/450 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -1.66 & 1.55 \\ 
  \textbf{Rodentia} & \textbf{species} & \textbf{90/2094} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & \textbf{2.76**} & \textbf{2.34**} \\ 
